\section{Business Logic}

For people who are going to continue the development of the business logic part of the server there are some things that might come in handy.

Learning how to use git in a proper way from the very beginning is of paramount importance. Set up a functioning branch structure and use pull requests to merge changes rather than just pushing or merging from origin master directly.

Git issues is an essential tool for keeping track of the current bugs and whatnot which we ended up using quite effectively as an formal communcation channel between groups.

As the three server groups are quite integrated with eachother make sure everyone is on the same page, preferably work in the same computer lab.

Remember to make integration tests for the program features. We have provided an integration test system in genomizer-server-tester.

Using Virtual machines with for example Vagrant is very useful when multiple groups want to test their features simultaneously. We used VM's on the server provided by the customer.

Kanban is a great way to keep track of your group members, what they're doing and what has to be done. 

Keep the reflections meetings fresh every time with new scrum reflection techniques that you can find online. use your imagination.

Be sure to take a brake, 3'o clock Fika is essential for everyone in the project to keep everyone happy and going strong. If possible take a breather at 10am as well.

Take your time to plan the whole sprint from the very start.
