\section{Data storage}

For developers who are going to continue the development of the database component there are some knowledge that might show useful.

Its a good idea to start with extracting the database dependency from the unittest suite. We quickly identified this as a potential issue, but did not think it was worth the effort during the project. In retrospect, this would have resulted in a lot smoother testing routines and would definitely have been worth the time invested.

There is a branch on Github named SRA_feature where we have started implementing a feature for downloading files from the Sequence Read Archive (SRA) database. In its current state it supports downloading remote RAW data files from SRA, however it is not yet fully implemented in or integrated with the rest of the system, and hence is not documented further throughout the remainder of this document.

We decided to try out pair programming (the agile software development technique) in the very first sprint and experienced surpringsingly good results.  We continued with this method throughout the remainder of the project and would recommend it working on projects of this size.

Working with Kanban is recommended, and using an actual physical board is preferable to digital versions (such as Trello) in our opinion. A physical board has a motivating factor and gives a better and quicker overview of what work is done and what work is still waiting for some action to be taken.

Establish a definition of done early.
